Hockey's Most Controversial Statistic: An Analysis of the Effectiveness of the Plus-Minus Statistic

### 2024-11-20 manuscript/statspaper.tex

\begin{abstract}
Here is the abstract.  
\end{abstract}

@@

In this paper, the effectiveness of the plus-minus statistic was evaluated to see if it is an effective predictor of player contribution
in the National Hockey League. The plus minus does have some value as a predictor of offensive and defensive metrics. However, other
advanced metrics like Corsi and Fenwick perform much better. The plus-minus is also heavily influenced by a player's team, making it 
less valuable as an indivual evaluator of player effectiveness. Overall, the NHL should maybe consider phasing out the use of the plus-minus
statistic and consider more advanced metrics such as Corsi or Fenwick.

>>>>

\begin{abstract}
The goal of this paper is to evaluate the plus minus statistic as a metric for determining the effectiveness of a player.
This involves analysing the relationship between a players plus-minus rating and other offensive and defensive ratings,
the effect of a players team performance on their plus-minus, and comparing plus-minus to other similar statistics. Based
on the analysis performed, the plus minus does have some value as a predictor of offensive and defensive metrics. However, other
advanced metrics like Corsi and Fenwick perform much better. The plus-minus is also heavily influenced by a player's team, making it 
less valuable as an indivual evaluator of player effectiveness.
\end{abstract}

@@

In this paper, the effectiveness of the plus-minus statistic was evaluated to see if it is an effective predictor of player contribution
in the National Hockey League. The plus minus does have some value as a predictor of offensive and defensive metrics. However, other
advanced metrics like Corsi and Fenwick perform much better. The plus-minus is also heavily influenced by a player's team, making it 
less valuable as an indivual evaluator of player effectiveness. Overall, the NHL should consider phasing out the use of the plus-minus
statistic and consider more advanced metrics such as Corsi or Fenwick.
